%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jonathan}{Ng} {\urlstyle{same} \href{mailto:jonathan.ng1@gmail.com
}{jonathan.ng1@gmail.com} | \href{http://t.me/derpy/}{@derpy}\\
\href{http://www.h1b1.com/practices/h-1b1-visa-for-chileans-singaporeans/}{H1B1 Eligible}
| +65 83995537
\\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.29\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NUS (National University of Singapore)}
\descript{BComp in Information Security}
\location{December 2021 | Singapore, SG}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/derpyplops}{\bf derpyplops} \\
LinkedIn://  \href{https://www.linkedin.com/in/jonathan-ng-7061a3162/}{\bf Jonathan Ng} \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
Python \textbullet{} Scala \textbullet{} VueJS  \\ 
JS  \textbullet{} SQL \textbullet{} React\\
\vspace{3mm}
\location{Familiar:}
Java\textbullet{} Shell \\ Golang \textbullet{} C++ \textbullet{} C \\
\sectionsep

\subsection{Tools \& Frameworks}
Apollo GQL \textbullet{} ZIO \textbullet{} Play Framework \\ AWS \textbullet{} GRPC \textbullet{} Jest \\ AsciiDoc \textbullet{} Redux \\ express.js \textbullet{} Kafka \textbullet{} Docker
\sectionsep

\subsection{Interests}
\textbf{Effective Altruism} \\
Arete Fellowship (SG) Organizer (Fall '20, Spring '21)\\
NUS Chapter Lead\\
\sectionsep

\subsection{Misc}
\textbf{ARENA} (\href{https://www.arena.education/}{arena.education})\\
\textbullet{} Implemented PPO, BERT, GPT (and more) from scratch. \\
\textbullet{} Contributed to TransformerLens, an open source library for interpretability research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.70\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

\runsubsection{Apart Research}
\descript{| Research Engineer (Contracting) }
\location{Apr 2024 – Present}
\vspace{\topsep}
\begin{tightemize}
\item First author on \emph{\textbf{Catastrophic Cyber Capabilities Benchmark (3CB): Robustly Evaluating LLM
Agent Cyber Offense Capabilities}} (pending review - ICLR '25)
\item Designed and implemented 11 complex cybersecurity LLM agent evals
\item Implemented multi-Docker agent evaluations in our agent LLM scaffolding
\item Wrote and conducted experiments across 14 language models, across Anthropic, OpenAI, TogetherAI, Replicate
\end{tightemize}
\sectionsep

\runsubsection{Surveyor}
\descript{| Sole Engineer }
\location{Oct 2023 – Present}
\begin{tightemize} 
\item Sole engineer building \href{https://surveyor.ink/}{Surveyor}, a webapp to build and deploy surveys. Backend, UX design, architecture and prompt engineering.
\item Implemented data pipeline for robustly parsing surveys from LM outputs, inclusive of conducting experiments and writing tests
\item Oversaw sub-contractor work on productionizing via containerization. \\> VueJS, TypeScript, Firestore DB, OpenAI API
\end{tightemize}
\sectionsep

\runsubsection{Cadenza Labs}
\descript{| Research Engineer }
\location{Apr 2023 – Present}
\begin{tightemize}
\item Developed the \href{https://github.com/EleutherAI/elk}{EleutherAI/elk} library, a white-box LLM interpretability library for training "truth-seeking" probes
\item Coordinated and conducted large sweeps across multiple GPU clusters, conducted original experiments
\end{tightemize}
\sectionsep

\runsubsection{SERI MATS}
\descript{| Research Engineer }
\location{Jan 2023 – March 2023 | Singapore}
\begin{tightemize}
\item Participated in seminars and workshops relating to AI Alignment, mentored by Dr Dan Hendrycks.
\item Authored the \emph{\textbf{Machiavelli}}
paper (ICML23), created a data collection platform on Streamlit (\href{https://github.com/derpyplops/cyoa-streamlit}{repo})
(\href{https://arxiv.org/abs/2304.03279}{paper}).
\item Worked with the trlx library to train LMs on an \href{https://github.com/hendrycks/ethics}{ethics} dataset via RLHF.

\end{tightemize}
\sectionsep
\runsubsection{LeadIQ}
\descript{| Software Engineer (Full-Stack) }
\location{Apr 2020 – June 2022 | Singapore}
\begin{tightemize}
\item Built Self-Serve Single Sign-On, a feature that automates SSO client setup, and cuts a 2-3 week long process down to a day. 
Won internal hackathon 1st place. After winning, we brought the code and made it production ready in a month.
\item Built Slack Bot delivering Job Change Notifications. \\ > \emph{Kafka, Scala, ZIO, Slack API}
\item Built Assign Sequences with Outreach.io API.\\ > \emph{Vue, CSS, HTML, ApolloGQL, Scala}
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage}
\end{document}  \documentclass[]{article}